### 2020-01-21 ChapterProblemDefinition/chapterProblemDefinition.tex
Fixed: Minor wording corrections in Problem Definition

In this chapter we will discuss the requirements of a solution to scalable real-time physics and the challenges of distributing a real-time physics engine, using a naive approach as an example. We will consider some potential solutions to distributing real-time physics and their trade-offs. Finally, we will describe our proposed solution (AP) along with high-level overviews of the challenges with this approach and our implemented and proposed solutions.

@@

We will now discuss the types of errors that can occur in distributed real-time physics simulations. Types of errors include time-space inconsistencies, in which two different objects occupy the same space at the same time, but on different servers.
Two objects occupying the same space at the same time, which can also lead to late collisions and missed collisions. 
Diverging results and object state conflict, in which the same object has different states on different servers, which can be caused by collision response results differing on different servers.
The same object having different states on different servers can lead to objects 'jittering', as the object state is conflicting between the two servers. 
Objects not being simulated (missed updates), can occur when objects are migrating between servers. Objects being duplicated and objects being lost. 
Examples and consequences of the above errors will now be described.

@@

\subsection{Object state conflict}
We will now discuss the challenges involved with two servers reaching a consensus on the state of an object if the two objects have conflicting states. If a solution is used in which two servers simulate the same object (such as in an overlapping region between servers), diverging results from collisions can result in the same object can end up in different states on different servers. These conflicts in state may be small, in which case they can be resolved by either choosing the state from one server or taking the average of the two objects, however, this may appear as `jitter' if the differences between states is large enough. Furthermore, cases may exist when the two states have diverged significantly, such as the stack of cubes example in \ref{divergingResults}, in which case averaging of the two states cannot be used. One server's state would have to be chosen, which would appear on the other server as though the objects have `teleported' (instantaneously changed position). In addition to this, prior to the server having its object's states overwritten, those objects may have affected other objects in only that server. For example, if we continue with the stack of cubes example in \ref{divergingResults}, suppose the stack of cubes fell over on one server and one of the cubes collided with a sphere, that is only being simulated by that sever (for example, if it is outside of the overlapping region). The sphere is given a velocity as a result of the collision. If the cubes in the stack are then updated to be the same as on a remote server, essentially rewriting the history of the cubes, the end result would be a stack of cubes that is upright and sphere with a velocity from a collision that has been effectively erased from the simulation history.

@@

\subsection{Missed updates}
Objects not being simulated (missed updates), can occur when objects are migrating between servers. When objects are being migrated between servers, they don't exist on any server, as a result the position and rotation of the object won't be updated. This would appear as though the object has frozen, how noticeable this would be to an observer would depend on the situation and the number of updates missed. For example, if the object is stationary or moving slowly, several time steps could be missed without be noticeable. Alternatively, in a scenario where a large object was in free-fall, very few update steps could be missed before an observer would notice that the object is not being simulated correctly.

>>>>

In this chapter the requirements of a solution to scalable real-time physics and the challenges of distributing a real-time physics engine will be discussed, using a naive approach as an example. Some potential solutions to distributing real-time physics and their trade-offs will be considered. Finally, our proposed solution (AP) will be described, along with high-level overviews of the challenges with this approach and our implemented and proposed solutions.

@@

The types of errors that can occur in distributed real-time physics simulations will now be discussed. 
Types of errors include:
\begin{itemize}
	\item Time-space inconsistencies, in which two different objects occupy the same space at the same time, but on different servers.
	\item Two objects occupying the same space at the same time, which can also lead to late collisions and missed collisions. 
	\item Diverging results and object state conflict, in which the same object has different states on different servers, which can be caused by collision response results differing on different servers.
	\item The same object having different states on different servers can lead to objects `jittering', as the object state is conflicting between the two servers. 
	\item Objects not being simulated (missed updates), which could occur when objects are migrating between servers. 
	\item Objects being duplicated and objects being lost. 
\end{itemize}

Examples and consequences of the above errors will now be described.

@@

\subsection{Object state conflict}
The challenges involved with two servers reaching a consensus on the state of an object if the two objects have conflicting states will now be discussed. If a solution is used in which two servers simulate the same object (such as in an overlapping region between servers), diverging results from collisions can result in the same object can end up in different states on different servers. These conflicts in state may be small, in which case they can be resolved by either choosing the state from one server or taking the average of the two objects, however, this may appear as `jitter' if the differences between states is large enough. Furthermore, cases may exist when the two states have diverged significantly, such as the stack of cubes example in \ref{divergingResults}, in which case averaging of the two states cannot be used. One server's state would have to be chosen, which would appear on the other server as though the objects have `teleported' (instantaneously changed position). In addition to this, prior to the server having its object's states overwritten, those objects may have affected other objects in only that server. For example, if we continue with the stack of cubes example in \ref{divergingResults}, suppose the stack of cubes fell over on one server and one of the cubes collided with a sphere, that is only being simulated by that sever (for example, if it is outside of the overlapping region). The sphere is given a velocity as a result of the collision. If the cubes in the stack are then updated to be the same as on a remote server, essentially rewriting the history of the cubes, the end result would be a stack of cubes that is upright and sphere with a velocity from a collision that has been effectively erased from the simulation history.

@@

\subsection{Missed updates}
Objects not being simulated (missed updates), can occur when objects are migrating between servers. When objects are being migrated between servers, they don't exist on any server, as a result the position and rotation of the object will not be updated. This would appear as though the object has frozen, how noticeable this would be to an observer would depend on the situation and the number of updates missed. For example, if the object is stationary or moving slowly, several time steps could be missed without be noticeable. Alternatively, in a scenario where a large object was in free-fall, very few update steps could be missed before an observer would notice that the object is not being simulated correctly.
